-

### 2023-02-02 DRAFT_homogeneous_impact_areas.Rmd

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tmap)
library(stars);packageVersion("stars")
library(units)
library(ggpubr)
library(DT)
library(tidyverse)
```

@@

```{r, echo=F}
# silently read cached file
path <- ifelse(dir == "C:", 
        "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds",
        "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds")
infra_stats <- readRDS(path)
```

Let's calculate the areas of these polygons and compare the HIF in the five regions. 
```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
infra_stats$area <- sf::st_area(infra_stats)

temp <- as.data.frame(infra_stats) %>%
  group_by(region, infrastructureIndex) %>%
  summarise(area = mean(area))

ggarrange(
  ggplot(temp, aes(x = region, y = area, fill = factor(infrastructureIndex)))+
    geom_bar(position = "stack", stat = "identity")+
    guides(fill = "none")+
    coord_flip()+
    xlab("")
  ,
  ggplot(temp, aes(x = region, y = area, fill = factor(infrastructureIndex)))+
    geom_bar(position = "fill", stat = "identity")+
    guides(fill = guide_legend("HIF"))+
    coord_flip()+
    xlab("")
)
```

@@

Here are the numbers behind the figure above.
```{r}
temp$area <- round(temp$area,0)
DT::datatable(temp)
```

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tmap)
library(stars);packageVersion("stars")
library(units)
library(ggpubr)
library(DT)
library(tidyverse)
library(units)
```

@@

```{r, include=F}
# silently read cached file
path <- ifelse(dir == "C:", 
        "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds",
        "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds")
infra_stats <- readRDS(path)
```

Let's calculate the areas of these polygons and compare the HIF in the five regions. 
```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
infra_stats$area_km2 <- units::drop_units(sf::st_area(infra_stats))
infra_stats$area_km2 <- infra_stats$area_km2/1000

temp <- as.data.frame(infra_stats) %>%
  group_by(region, infrastructureIndex) %>%
  summarise(area_km2 = mean(area_km2))

ggarrange(
  ggplot(temp, aes(x = region, y = area_km2, fill = factor(infrastructureIndex)))+
    geom_bar(position = "stack", stat = "identity")+
    guides(fill = "none")+
    coord_flip()+
    xlab("")
  ,
  ggplot(temp, aes(x = region, y = area_km2, fill = factor(infrastructureIndex)))+
    geom_bar(position = "fill", stat = "identity")+
    guides(fill = guide_legend("HIF"))+
    coord_flip()+
    ylab("Fraction of total area")+
    xlab("")
)
```

@@

Here are the numbers behind the figure above.
```{r}
temp$area_km2 <- round(temp$area_km2,0)
DT::datatable(temp)
```
